\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2013-01-07 resubmit_mnras2/response.txt

To whom it may concern,

The reviewer only requested minor changes to one section of the
paper. We agree with their suggestions and have implemented them.

We have provided a version of the manuscript processed with
"latexdiff" to highlight the differences between the previous version
(removed text in red) and the newly resubmitted version (added text in
blue) with the supplementary material
(diff_resubmission_resubmission2.pdf). As the reviewer did not request to
see this new version, we have not uploaded new versions of the
companion papers (Holland et al., and Dempsey et al.), although this
can easily be done if requested.

Detailed responses to the referee's comments are
provided below, preceded by "*".

Dear Dr Chapin

I attach the reviewer's comments on your revised manuscript entitled "SCUBA-2: iterative map-making with the Sub-Millimetre User Reduction Facility", ref. MN-12-2293-MJ.R1, which you submitted to Monthly Notices of the Royal Astronomical Society.

Some further, minor revision of your manuscript is requested before it is reconsidered for publication.

You should submit your further revised version, together with your response to the reviewer's comments via the Monthly Notices ScholarOne Manuscripts site http://mc.manuscriptcentral.com/mnras .
Enter your Author Centre, where you will find your manuscript title listed under "Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your manuscript reference will be appended to denote a revision.

IMPORTANT: do not submit your revised manuscript as a new paper!

You will not be able to make your revisions to the originally submitted files of the manuscript on ScholarOne Manuscripts. Instead, you must delete the original files and abstract and replace them with your revised files. Carefully proof read the resulting PDF and HTML files that are generated. If you have used a .bib file to generate your bibliography in Latex, please include this in your .tar archive along with the .bbl and .tex files; this will aid the editing and typesetting process.

When submitting your revised manuscript, you will be able to respond to the comments made by the reviewer in the space provided. You should also use this space to document any changes you make to the original manuscript. In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the reviewer. It would also be very helpful if you could highlight the changed sections, e.g. by the use of colour, colour highlighting or bold typeface - this will not delay in any way the subsequent processing of your paper.

Because we are trying to facilitate timely publication of manuscripts submitted to MNRAS, your revised manuscript should be uploaded promptly. If you do not submit your revision within six months, we may consider it withdrawn and request it be resubmitted as a new submission.

Please note that, due to the tight schedule, any post-acceptance changes notified after the paper has gone into production (i.e. the day after the acceptance email is sent) cannot be incorporated into the paper before it is typeset. Such changes will therefore need to be made as part of the proof corrections. To avoid excessive proof corrections and the delay that these can cause, you are strongly encouraged to ensure that each version of your paper submitted to MNRAS is completely ready for publication!

I look forward to receiving your revised manuscript.

Regards,

Keith

-- 
Dr Keith T. Smith

Assistant Editor (MNRAS)
Royal Astronomical Society
Burlington House
Piccadilly
London W1J 0BQ

cc: all S1M-listed co-authors.

Reviewer's Comments:

I commend the authors on a careful revision. I am happy the first review was useful. Reading through the corrections and the new revision, nearly everything makes sense to me now. The new section 3.4 gives a useful snapshot of reality to the SMURF user. The new atmosphere descriptions are also illuminating. Sorry to hear about the less than useful DKS (added text appreciated). The confusion in section 4 over the masking, filtering and degeneracies is all cleared up nicely.

I had only one hang-up in the matched filter section (the history of which is reproduced and expounded on below). Given your careful attention to the first review, I'm happy to leave this to your good judgement and do not require another look (unless you request it).

+ Sec 4.2, Para 8: "For the case at hand, the effective PSF for the whitened maps is given by the dotted curve in Fig. 13."

This is confusing language. Fig 13 list the dashed line as "whitened". It is true though that the dotted curve gives the correct PSF for your matched filter, since it's the one that corresponds to the pre-filtered beam. The matched filter in Fourier space is B(k)N^-1(k), where the N^-1(k) is your pre-whitening step (dividing by the power spectrum of the noise). The B(k) is the PSF before the whitening. It seems like you say this here, but it's a bit confusing with the figure labeling. Maybe it would be useful to include a simple equation like \Phi(k) = B(k)N^-1(k) or similar to describe your total operation?

- Yes, we are essentially breaking down the typical B(k)/N^-1(k)
matched-filter expression into two steps. We've clarified the text
here.

-- I follow this, though there may still be a confusing bit. In the added text: "Next, the Fourier transform of map filtered PSF is divided by the jackknife noise power spectrum to calculate the final whitened PSF (dashed line in Fig. 14)." In whitening the map you say "The filter is applied by scaling the power spectrum of the map by this function and then transforming back into real space." In order to retain phase information in the map, I'm guessing this sentence means you take the FT of the map and divide by the sqrt of the power spectrum of the jack knife and the transform back? The PS of such a map would in theory be white if it were all noise. If this is the case then I would have guessed that the "map filtered PSF is divided by the [sqrt of the] jackknife noise power spectrum to calculate the final whitened PSF". Taking N(k) as the power spectrum of the noise (or equivalently jackknife estimate of noise), this gives the right form of a matched filter B(k)/N(k) where a factor of 1/sqrt(N) comes from the whitening and another factor of B(k)/sqrt(N) comes from the "PSF" filtering. The only other qualm that comes to mind is that by including the 1/sqrt(N) in the PSF "matched filter" step, the claim in the text that it is an optimal *low-pass* filter is not really true. Since 1/sqrt(N) suppresses large scales for a "red" N, the matched filter is a *band-pass* filter. Said in another way, you have to start with a map with white noise to have the matched filter be a simple PSF that low-pass filters the map (presumably as would be the case in most optical datasets). One can't tag on a pre-whitening step to data with non-white noise and describe the match filter of the "whitened" map as a simple smoothing filter.

* Yes, as you point our we are in fact dividing the Fourier Transform
  coefficients by the square-root of the jackknife estimate of the
  noise power spectrum. This is now written correctly in the caption
  of Fig.14, as well as paragraphs 6 and 7 of Section 4.2.

* We have also changed and moved the text about "optimal low pass
  filtering" to the end of paragraph 7, and instead refer to it as a
  "band pass" filter to summarize the entire operation, as you have
  correctly suggested.

### 2013-01-15 arXiv_submission/smurf_paper.tex
minor fiddles for arXiv submission

%------------------------------------------------------------------------------
% SMURF Paper
%------------------------------------------------------------------------------

\documentclass[useAMS,usenatbib,nofootinbib]{mn2e}

@@

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2012} is a new instrument for the 15-m James
Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
simultaneously images the sky in two broad bands centred over 450 and
850\,\micron, with approximately 7.5 and 14.5\,arcsec full-width at
half-maximum (FWHM) point spread functions (PSFs). The focal planes at
each wavelength are populated with 4 rectangular subarrays, consisting
of $40 \times 32$ bolometers each, and together subtend a nearly
7\,arcmin $\times$ 7\,arcmin footprint on the sky (excluding gaps, the
continuous solid angle is about 43\,arcmin$^{2}$ per focal plane).
This paper describes the properties of \scuba\ data that are relevant
for producing maps of the imaging data, and the Submillimetre User
Reduction Facility, SMURF, a software package for performing the
reduction written using the Starlink Software Environment
\citep{1993ASPC...52..229W,2009ASPC..411..418J}. The details of the
instrument design, performance, and calibration are given in two
companion papers: \citet{holland2012} and \citet{dempsey2012}.

Over the last twenty years, observations in the submillimetre band
(defined here to be 200--1200\,\micron) have helped revolutionise
several important areas of astrophysics, including: discovering
through blind surveys a class of massive dusty star-forming galaxies
in the early ($z>2$) Universe, now referred to as submillimetre
galaxies, or SMGs; the characterisation of the early stages of
star-formation by identifying the dense, cold regions in molecular
clouds where stars may eventually form; and identifying debris disks
around nearby stars, helping us understand the early stages of planet
formation.  With $10,240$ nominal detectors \citep[of which $\sim$70\%
work and are typically useful,][]{holland2012}, \scuba\ is presently
the largest of a new generation of multiplexed kilopixel
(sub)millimetre bolometer cameras, which also includes the cameras for
the South Pole Telescope \citep[SPT,][]{carlstrom2011} and the Atacama
Cosmology Telescope \citep[ACT,][]{swetz2011}, both dedicated
experiments for studying anisotropies in the Cosmic Microwave
Background (CMB) using similar technology, the latter of which uses the
same time-domain multiplexed readout electronics as \scuba\
\citep{battistelli2008}.

@@

While the details of how \scuba\ works are described in
\citet{holland2012}, and its calibration in \citet{dempsey2012}, we
summarise the basic concepts relevant to map-making here.

Incoming light passes through a beam-splitter, and then bandpass
filters, providing simultaneous illumination and wavelength definition
of both the 450 and 850\,\micron\ focal planes. Each focal plan is
populated by four ``subarrays'' (labelled s4a--s4d at 450\,\micron, and
s8a--s8d at 850\,\micron), each consisting of 32 columns and 40 rows
of bolometers. The bolometers are thermal absorbers (with a response
time constant of $\tau \sim 1$\,ms) coupled to superconducting
transition-edge sensors (TESs) for thermometry. Temperature variations
in the TESs produce changing currents, and therefore varying magnetic
fields, which are detected and amplified using chains of
superconducting quantum interference devices (SQUIDs), before the
larger output currents are digitised. Each detector has its own SQUID
for the first-stage of the amplification, but the remaining stages
occur within a common chain of SQUIDs for each of the 32 columns. All
40 rows are read out in sequence at a row-visit frequency of about
12\,kHz. Such a high sample rate is unnecessary to produce maps, so
the data are re-sampled to approximately 200\,Hz before writing to
disk. This rate provides a sample every 3.0\,arcsec, or approximately
one third of the 450\,\micron\ diffraction-limited full-width at
half-maximum (FWHM) -- a typical rule-of-thumb for adequately sampling
a Gaussian point spread function (PSF) -- at the maximum scanning
speed of 600\,arcsec\,s$^{-1}$. There is an additional 41st row of
SQUID readouts that are not connected to TESs. These ``dark SQUIDs''
track non-thermal noise sources that are common to each column's
amplifier chain. The relationship between the output digitised
current, $I$, and the input power, $P$, or $dI/dP$ is established
using flatfield observations immediately prior to science
observations, in which the output signal is measured throughout a ramp
of the pixel heaters (which provide a known input power); see
Section~2.1 in \citet{dempsey2012} and Section~5.3 in
\citet{holland2012} for more details. Finally, the conversion to
astronomical flux units from power involves a correction for
atmospheric extinction \citep[primarily using the 183\,GHz (1.6\,mm)
JCMT Water Vapour Monitor to track line-of-sight opacity variations,
see Section~3 in][]{dempsey2012}, and the application of a flux
conversion factor (FCF) which is established from regular measurements
of calibrators such as Uranus \citep[Section~5 in][]{dempsey2012}.

@@

We note that the noise performance of \scuba\ has evolved over
time. An initial ``\scuba\ shared-risk observing'' period (S2SRO) took
place during February and March 2010, during which each of the 450 and
850\,\micron\ focal planes were populated with single subarrays, s4a
and s8d, respectively. In addition to having significantly fewer
available bolometers than the current fully-commissioned instrument
(and therefore a mapping speed reduced by a factor of $\sim$4),
instabilities in the fridge led to a large periodic signal with a
period of about 25\,s that was correlated amongst the detectors. After
upgrading and commissioning the instrument, a servo using newly added
thermometers in the focal planes has effectively mitigated this
problem \citep[Section~2.5 in][]{holland2012}. In addition, there were
improvements to the magnetic shielding (reducing magnetic field
pickup, as described in Section~\ref{sec:magpickup}), as well as more
effective removal of aliased noise sources (which has reduced both the
presence of line features and the mean white noise level).

In order to reduce the impact of low-frequency noise on the final
maps, \scuba\ scan strategies have been designed to provide: (i) good
cross-linking (visiting every point of the mapped area at different
scan angles); and (ii) minimal accelerations to reduce turn-around
overheads (which could be quite large given the 600\,arcsec\,s$^{-1}$
maximum scan speed). For areas larger than the array footprint a
rectangular ``PONG'' pattern is used, in which the boresight travels
in approximately straight lines and ``bounces'' off the edges at
45\,degree angles until the area is uniformly filled in. It is also
usually combined with a rotation through a number of fixed position
angles to create a ``rotating PONG'' with even better
cross-linking. For smaller areas (of order the array footprint, or
point sources), in which the PONG turn-around overheads would be
large, a ``constant velocity daisy'' (CV Daisy) is used.  Here the
telescope moves in a circle, whose centre also slowly traces out a
small circle. For a more complete description of the \scuba\ observing
modes, see Section~5 in \citet{holland2012} and also
\citet{2010SPIE.7740E..66K}.

@@

Prior to executing the iterative part of the algorithm, the data must
undergo several pre-processing steps. First, the data files are read
into memory and concatenated into continuous arrays (\scuba\ data are
broken up and written to disk every $\sim$30\,s regardless of the
observation length during data acquisition). As the data are loaded,
they are multiplied by the flatfield correction \citep[see Section~2.1
in][]{dempsey2012}. Next, a series of configurable data cleaning and
filtering procedures are applied; these include the removal of large
glitches that may hinder the iterative solution from converging, or
simply tasks that do not need to be iterated. All of the data that are
flagged as bad are ignored when estimating the map.

@@

Sudden steps can occur in the time-series data from each bolometer,
with the most likely cause being cosmic ray events \citep[see
Section~3.5.3 in][]{holland2012}. The black curves in
Fig.~\ref{fig:steps1} show examples of such steps in the time-series
for two bolometers. If not removed, these steps can cause severe
ringing when filtering, and visible streaks in the final map,
corresponding to the paths of individual bolometers over the sky.

@@

The extinction correction is a multiplicative factor that is normally
derived using the WVM, and is not considered to be a free parameter in
the solution [$\mathbf{e}_i(t)$ in Eq.~\ref{eq:model}]. However, it is
applied as part of the iterative solution, rather than a
pre-processing step, since any small errors will be amplified by the
large low-frequency drifts in the raw bolometer time-series. For
example, if the bolometer drift is 1000 times greater than an
astronomical source of interest, a 1 per cent error in the flatfield
will produce stripes of order 10 times the astronomical signal
amplitude in the final map! If \model{EXT} is applied after the bulk
of the low-frequency noise has been removed (e.g., \model{COM,GAI}),
then there is little potential for such small errors to affect the
final map.  For details on how it is calculated see
\citet{dempsey2012}. Note that its numerical value is calculated only
once, and simply applied as a scale factor in the iterative
solution. Unlike the additive model components, it is inverted at the
start of each iteration to preserve the amplitude of the data before
the re-calculation of other model components.

@@

The white noise levels of \scuba\ bolometers are measured between 2
and 10\,Hz in the PSDs (as described in Section~\ref{sec:noi}),
leading to noise equivalent powers (NEPs, with units W\,s$^{1/2}$) --
the \rms\ time-series noise in a 1\,s integration \citep[see section
3.5.2 in][]{holland2012}. The NEPs are then converted into more useful
noise equivalent flux densities (NEFDs, with units Jy\,s$^{1/2}$)
through multiplication by the extinction correction and the FCF. For
an ideal scan pattern in which every bolometer spends an equal amount
of time observing each point on the sky, the expected noise in a map
pixel is $\mathrm{NEFD_{eff}}/t^{1/2}$, where $t$ is the integration
time, and the effective NEFD, $\mathrm{NEFD_{eff}} = (1/\sum
\mathrm{NEFD}_i^{-2})^{1/2}$, is the sensitivity of the entire array
including all bolometers $i$. Experimentally it has been found that
the map noise based on the weighted scatter of the data
(Eq.~\ref{eq:varmap}), and the scatter of map pixels in small
apertures, both correlate well with this expected limiting noise
performance for maps that are larger than the array footprint (for
smaller maps the assumption of uniform coverage is incorrect). As an
example of observing under favourable conditions with line-of-sight
opacities of 0.87 and 0.34 at 450 and 850\,\micron\ \citep[zenith sky
opacities at 225\,GHz of 0.04 and 0.065 at 450 and 850\,\micron,
respectively, at an average airmass of 1.2, from table 3
in][]{holland2012}, the mapping speed is approximately
$6\times10^{-5}$ and $3\times10^{-3}$\,deg$^2$\,hr$^{-1}$\,mJy$^{-2}$,
at 450 and 850\micron, for the default pixel sizes of 2 and 4\,arcsec,
respectively. If maps are filtered and cross-correlated with the PSF
for the optimal extraction of point sources (see
Section~\ref{sec:cosmo}), the mapping speeds increase to approximately
$5\times10^{-4}$ and
$1.5\times10^{-2}$\,deg$^2$\,hr$^{-1}$\,mJy$^{-2}$ in this example,
independently of the chosen map pixel sizes. See the on-line \scuba\
integration time calculator for mapping speeds under arbitrary
observing conditions and scan
modes\footnote{\url{http://www.jach.hawaii.edu/jac-bin/propscuba2itc.pl}}.

@@

This example illustrates the need for constraints in the map solution
in many situations. For calibrators (and other previously known
bright, compact sources), a good, simple prior is to constrain the map
to a value of zero away from the known locations of emission (part of
the \model{AST} model calculation, Section~\ref{sec:ast}).  In
Fig.~\ref{fig:pointmaps}d, a solution is produced in an identical
manner to Fig.~\ref{fig:pointmaps}c, but now setting the map
explicitly to zero beyond a radius of 60\,arcsec from the location of
Uranus (much larger than the FWHM of the main lobe), for all but the
final iteration. In this case, the map converges after 6 iterations,
and the ringing has been effectively removed. The attenuation from the
previous reduction is now removed, and Uranus again has a peak value
of 0.358\,pW. For reference, the Uranus model distributed with
Starlink predicts a peak brightness of 176\,Jy on this date, yielding
an FCF of 491 Jy\,pW$^{-1}$, which is well within the typical range
for \scuba\ of $(492 \pm 67)$\,Jy\,pW$^{-1}$ \citep[see][for
details]{dempsey2012}. Since the map is now flat away from the source,
and constrained to a value of zero, it is appropriate for performing
aperture photometry directly, with no need for an additional reference
annulus.

>>>>

%------------------------------------------------------------------------------
% SMURF Paper
%------------------------------------------------------------------------------
\pdfoutput=1
\documentclass[useAMS,usenatbib,nofootinbib]{mn2e}

@@

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2013} is a new instrument for the 15-m James
Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
simultaneously images the sky in two broad bands centred over 450 and
850\,\micron, with approximately 7.5 and 14.5\,arcsec full-width at
half-maximum (FWHM) point spread functions (PSFs). The focal planes at
each wavelength are populated with 4 rectangular subarrays, consisting
of $40 \times 32$ bolometers each, and together subtend a nearly
7\,arcmin $\times$ 7\,arcmin footprint on the sky (excluding gaps, the
continuous solid angle is about 43\,arcmin$^{2}$ per focal plane).
This paper describes the properties of \scuba\ data that are relevant
for producing maps of the imaging data, and the Submillimetre User
Reduction Facility, SMURF, a software package for performing the
reduction written using the Starlink Software Environment
\citep{1993ASPC...52..229W,2009ASPC..411..418J}. The details of the
instrument design, performance, and calibration are given in two
companion papers: \citet{holland2013} and \citet{dempsey2013}.

Over the last twenty years, observations in the submillimetre band
(defined here to be 200--1200\,\micron) have helped revolutionise
several important areas of astrophysics, including: discovering
through blind surveys a class of massive dusty star-forming galaxies
in the early ($z>2$) Universe, now referred to as submillimetre
galaxies, or SMGs; the characterisation of the early stages of
star-formation by identifying the dense, cold regions in molecular
clouds where stars may eventually form; and identifying debris disks
around nearby stars, helping us understand the early stages of planet
formation.  With $10,240$ nominal detectors \citep[of which $\sim$70\%
work and are typically useful,][]{holland2013}, \scuba\ is presently
the largest of a new generation of multiplexed kilopixel
(sub)millimetre bolometer cameras, which also includes the cameras for
the South Pole Telescope \citep[SPT,][]{carlstrom2011} and the Atacama
Cosmology Telescope \citep[ACT,][]{swetz2011}, both dedicated
experiments for studying anisotropies in the Cosmic Microwave
Background (CMB) using similar technology, the latter of which uses the
same time-domain multiplexed readout electronics as \scuba\
\citep{battistelli2008}.

@@

While the details of how \scuba\ works are described in
\citet{holland2013}, and its calibration in \citet{dempsey2013}, we
summarise the basic concepts relevant to map-making here.

Incoming light passes through a beam-splitter, and then bandpass
filters, providing simultaneous illumination and wavelength definition
of both the 450 and 850\,\micron\ focal planes. Each focal plan is
populated by four ``subarrays'' (labelled s4a--s4d at 450\,\micron, and
s8a--s8d at 850\,\micron), each consisting of 32 columns and 40 rows
of bolometers. The bolometers are thermal absorbers (with a response
time constant of $\tau \sim 1$\,ms) coupled to superconducting
transition-edge sensors (TESs) for thermometry. Temperature variations
in the TESs produce changing currents, and therefore varying magnetic
fields, which are detected and amplified using chains of
superconducting quantum interference devices (SQUIDs), before the
larger output currents are digitised. Each detector has its own SQUID
for the first-stage of the amplification, but the remaining stages
occur within a common chain of SQUIDs for each of the 32 columns. All
40 rows are read out in sequence at a row-visit frequency of about
12\,kHz. Such a high sample rate is unnecessary to produce maps, so
the data are re-sampled to approximately 200\,Hz before writing to
disk. This rate provides a sample every 3.0\,arcsec, or approximately
one third of the 450\,\micron\ diffraction-limited full-width at
half-maximum (FWHM) -- a typical rule-of-thumb for adequately sampling
a Gaussian point spread function (PSF) -- at the maximum scanning
speed of 600\,arcsec\,s$^{-1}$. There is an additional 41st row of
SQUID readouts that are not connected to TESs. These ``dark SQUIDs''
track non-thermal noise sources that are common to each column's
amplifier chain. The relationship between the output digitised
current, $I$, and the input power, $P$, or $dI/dP$ is established
using flatfield observations immediately prior to science
observations, in which the output signal is measured throughout a ramp
of the pixel heaters (which provide a known input power); see
Section~2.1 in \citet{dempsey2013} and Section~5.3 in
\citet{holland2013} for more details. Finally, the conversion to
astronomical flux units from power involves a correction for
atmospheric extinction \citep[primarily using the 183\,GHz (1.6\,mm)
JCMT Water Vapour Monitor to track line-of-sight opacity variations,
see Section~3 in][]{dempsey2013}, and the application of a flux
conversion factor (FCF) which is established from regular measurements
of calibrators such as Uranus \citep[Section~5 in][]{dempsey2013}.

@@

We note that the noise performance of \scuba\ has evolved over
time. An initial ``\scuba\ shared-risk observing'' period (S2SRO) took
place during February and March 2010, during which each of the 450 and
850\,\micron\ focal planes were populated with single subarrays, s4a
and s8d, respectively. In addition to having significantly fewer
available bolometers than the current fully-commissioned instrument
(and therefore a mapping speed reduced by a factor of $\sim$4),
instabilities in the fridge led to a large periodic signal with a
period of about 25\,s that was correlated amongst the detectors. After
upgrading and commissioning the instrument, a servo using newly added
thermometers in the focal planes has effectively mitigated this
problem \citep[Section~2.5 in][]{holland2013}. In addition, there were
improvements to the magnetic shielding (reducing magnetic field
pickup, as described in Section~\ref{sec:magpickup}), as well as more
effective removal of aliased noise sources (which has reduced both the
presence of line features and the mean white noise level).

In order to reduce the impact of low-frequency noise on the final
maps, \scuba\ scan strategies have been designed to provide: (i) good
cross-linking (visiting every point of the mapped area at different
scan angles); and (ii) minimal accelerations to reduce turn-around
overheads (which could be quite large given the 600\,arcsec\,s$^{-1}$
maximum scan speed). For areas larger than the array footprint a
rectangular ``PONG'' pattern is used, in which the boresight travels
in approximately straight lines and ``bounces'' off the edges at
45\,degree angles until the area is uniformly filled in. It is also
usually combined with a rotation through a number of fixed position
angles to create a ``rotating PONG'' with even better
cross-linking. For smaller areas (of order the array footprint, or
point sources), in which the PONG turn-around overheads would be
large, a ``constant velocity daisy'' (CV Daisy) is used.  Here the
telescope moves in a circle, whose centre also slowly traces out a
small circle. For a more complete description of the \scuba\ observing
modes, see Section~5 in \citet{holland2013} and also
\citet{2010SPIE.7740E..66K}.

@@

Prior to executing the iterative part of the algorithm, the data must
undergo several pre-processing steps. First, the data files are read
into memory and concatenated into continuous arrays (\scuba\ data are
broken up and written to disk every $\sim$30\,s regardless of the
observation length during data acquisition). As the data are loaded,
they are multiplied by the flatfield correction \citep[see Section~2.1
in][]{dempsey2013}. Next, a series of configurable data cleaning and
filtering procedures are applied; these include the removal of large
glitches that may hinder the iterative solution from converging, or
simply tasks that do not need to be iterated. All of the data that are
flagged as bad are ignored when estimating the map.

@@

Sudden steps can occur in the time-series data from each bolometer,
with the most likely cause being cosmic ray events \citep[see
Section~3.5.3 in][]{holland2013}. The black curves in
Fig.~\ref{fig:steps1} show examples of such steps in the time-series
for two bolometers. If not removed, these steps can cause severe
ringing when filtering, and visible streaks in the final map,
corresponding to the paths of individual bolometers over the sky.

@@

The extinction correction is a multiplicative factor that is normally
derived using the WVM, and is not considered to be a free parameter in
the solution [$\mathbf{e}_i(t)$ in Eq.~\ref{eq:model}]. However, it is
applied as part of the iterative solution, rather than a
pre-processing step, since any small errors will be amplified by the
large low-frequency drifts in the raw bolometer time-series. For
example, if the bolometer drift is 1000 times greater than an
astronomical source of interest, a 1 per cent error in the flatfield
will produce stripes of order 10 times the astronomical signal
amplitude in the final map! If \model{EXT} is applied after the bulk
of the low-frequency noise has been removed (e.g., \model{COM,GAI}),
then there is little potential for such small errors to affect the
final map.  For details on how it is calculated see
\citet{dempsey2013}. Note that its numerical value is calculated only
once, and simply applied as a scale factor in the iterative
solution. Unlike the additive model components, it is inverted at the
start of each iteration to preserve the amplitude of the data before
the re-calculation of other model components.

@@

The white noise levels of \scuba\ bolometers are measured between 2
and 10\,Hz in the PSDs (as described in Section~\ref{sec:noi}),
leading to noise equivalent powers (NEPs, with units W\,s$^{1/2}$) --
the \rms\ time-series noise in a 1\,s integration \citep[see section
3.5.2 in][]{holland2013}. The NEPs are then converted into more useful
noise equivalent flux densities (NEFDs, with units Jy\,s$^{1/2}$)
through multiplication by the extinction correction and the FCF. For
an ideal scan pattern in which every bolometer spends an equal amount
of time observing each point on the sky, the expected noise in a map
pixel is $\mathrm{NEFD_{eff}}/t^{1/2}$, where $t$ is the integration
time, and the effective NEFD, $\mathrm{NEFD_{eff}} = (1/\sum
\mathrm{NEFD}_i^{-2})^{1/2}$, is the sensitivity of the entire array
including all bolometers $i$. Experimentally it has been found that
the map noise based on the weighted scatter of the data
(Eq.~\ref{eq:varmap}), and the scatter of map pixels in small
apertures, both correlate well with this expected limiting noise
performance for maps that are larger than the array footprint (for
smaller maps the assumption of uniform coverage is incorrect). As an
example of observing under favourable conditions with line-of-sight
opacities of 0.87 and 0.34 at 450 and 850\,\micron\ \citep[zenith sky
opacities at 225\,GHz of 0.04 and 0.065 at 450 and 850\,\micron,
respectively, at an average airmass of 1.2, from table 3
in][]{holland2013}, the mapping speed is approximately
$6\times10^{-5}$ and $3\times10^{-3}$\,deg$^2$\,hr$^{-1}$\,mJy$^{-2}$,
at 450 and 850\micron, for the default pixel sizes of 2 and 4\,arcsec,
respectively. If maps are filtered and cross-correlated with the PSF
for the optimal extraction of point sources (see
Section~\ref{sec:cosmo}), the mapping speeds increase to approximately
$5\times10^{-4}$ and
$1.5\times10^{-2}$\,deg$^2$\,hr$^{-1}$\,mJy$^{-2}$ in this example,
independently of the chosen map pixel sizes. See the on-line \scuba\
integration time calculator for mapping speeds under arbitrary
observing conditions and scan
modes\footnote{\url{http://www.jach.hawaii.edu/jac-bin/propscuba2itc.pl}}.

@@

This example illustrates the need for constraints in the map solution
in many situations. For calibrators (and other previously known
bright, compact sources), a good, simple prior is to constrain the map
to a value of zero away from the known locations of emission (part of
the \model{AST} model calculation, Section~\ref{sec:ast}).  In
Fig.~\ref{fig:pointmaps}d, a solution is produced in an identical
manner to Fig.~\ref{fig:pointmaps}c, but now setting the map
explicitly to zero beyond a radius of 60\,arcsec from the location of
Uranus (much larger than the FWHM of the main lobe), for all but the
final iteration. In this case, the map converges after 6 iterations,
and the ringing has been effectively removed. The attenuation from the
previous reduction is now removed, and Uranus again has a peak value
of 0.358\,pW. For reference, the Uranus model distributed with
Starlink predicts a peak brightness of 176\,Jy on this date, yielding
an FCF of 491 Jy\,pW$^{-1}$, which is well within the typical range
for \scuba\ of $(492 \pm 67)$\,Jy\,pW$^{-1}$ \citep[see][for
details]{dempsey2013}. Since the map is now flat away from the source,
and constrained to a value of zero, it is appropriate for performing
aperture photometry directly, with no need for an additional reference
annulus.
